Learning semi-Markovian DAGs with flow-based VAE

### 2023-12-11 Tex/slide.tex
slide 오류수정

\begin{frame}[allowframebreaks]{Dependent Noise}
    Proportion of bidirectional edges fixed to 0.3.
    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}
                \centering
                \includegraphics[width=\textwidth]{fig/SHD_dependence_30_DAG_threshold0.3.pdf}
                \caption{SHD with dependent Gaussian}
                \label{fig:dep_gaussian_shd}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{figure}
                \centering
                \includegraphics[width=\textwidth]{fig/FDR_dependence_30_DAG_threshold0.3.pdf}
                \caption{FDR with dependent Gaussian}
                \label{fig:dep_gaussian_fdr}
            \end{figure}
        \end{column}
    \end{columns}

    Proportion of bidirectional edges fixed to 0.3.
    \begin{figure}
        \centering
        \includegraphics[height=4cm]{fig/Predicted Edges_dependence_30_DAG_threshold0.3.pdf}
        \caption{Number of predicted edges with dependent Gaussian}
        \label{fig:dep_gaussian_edges}
    \end{figure}
    \begin{itemize}
        \item In the case of dependent Gaussian noise, our method(blue) performs better than DAG-GNN(orange).
        \item Considering the stable number of predicted edges with the SHD and FDR, our method(blue) outperforms.
    \end{itemize}

>>>>

\begin{frame}[allowframebreaks]{Dependent Noise}
    Proportion of bidirectional edges fixed to 0.3.
    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}
                \centering
                \includegraphics[width=\textwidth]{fig/SHD_dependence_30.pdf}
                \caption{SHD with dependent Gaussian}
                \label{fig:dep_gaussian_shd}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{figure}
                \centering
                \includegraphics[width=\textwidth]{fig/FDR_dependence_30.pdf}
                \caption{FDR with dependent Gaussian}
                \label{fig:dep_gaussian_fdr}
            \end{figure}
        \end{column}
    \end{columns}

    Proportion of bidirectional edges fixed to 0.3.
    \begin{figure}
        \centering
        \includegraphics[height=4cm]{fig/Predicted Edges_dependence_30.pdf}
        \caption{Number of predicted edges with dependent Gaussian}
        \label{fig:dep_gaussian_edges}
    \end{figure}
    \begin{itemize}
        \item In the case of dependent Gaussian noise, our method(blue) performs better than DAG-GNN(orange).
        \item Considering the stable number of predicted edges with the SHD and FDR, our method(blue) outperforms.
    \end{itemize}
